This section introduces some overlap with section \ref{sec:usage} in an attempt to list all the configuration options and elaborate on their meaning where they have not been discussed so far and a discussion is required.

\subsubsection{Proxy parameters}

\texttt{socksProxyHost=127.0.0.1} \\
\texttt{proxySet=true} \\
\texttt{socksProxyPort=1080} \\

\subsubsection{Flashlist database settings}

\texttt{flashlistDbMode=read} \\

Actually only mySQL is fully supported as database type and only in this case the database engine setting makes sense. \\
\texttt{flashlistDbType=mysql} \\
\texttt{flashlistDbEngine=myisam} \\

\texttt{flashlistDbHost=localhost} \\
\texttt{flashlistDbUser=load} \\
\texttt{flashlistDbPass=your\_password} \\
\texttt{flashlistDbName=flashlists\_rest} \\

This option indicates which column, in each table, is the time of fetching particular row. This value is later used for playback. \\
\texttt{retrievalTimestampName=fetchstamp} \\

This option determines whether the retrieval timestamp column should be indexed when initializing a database based on the dump files \\
\texttt{flashlistDbIndexTimestamps=true} \\

\subsubsection{Online flashlists setting}

\texttt{onlineFlashlistsRoot[0]=http://srv-c2d04-19.cms:9941/urn:xdaq-application:lid=400/} \\
\texttt{onlineFlashlistsRoot[1]=http://srv-c2d04-19.cms:9942/urn:xdaq-application:lid=400/} \\

\subsubsection{Dumped flashlists}\label{subsec:dumps}
The directories listed using the option below are scanned in search of the flashlist dump files that will be used to create and fill database.

\texttt{flashlistForDbDir[0]=/depot/flashlists13.11/} \\
\texttt{flashlistForDbDir[1]=/depot/flashlists13.11\_2/} \\
\texttt{flashlistForDbDir[2]=/depot/flashlists13.11\_3/} \\
\texttt{flashlistForDbDir[0]=/depot/flashlists13.11\_4/} \\
\texttt{flashlistForDbDir[0]=/home/bawey/Desktop/flmini/flashlistsExport} \\
\texttt{flashlistForDbDir[2]=/home/bawey/Desktop/flashlists/41} \\


\subsubsection{EPL directories}
\texttt{eplDir[0]=epl} \\
\texttt{eplDir[1]=epl\_test}\\


\subsubsection{Output modules}
\texttt{view[0]=ThroughputMonitor} \\
\texttt{view[1]=FileSink} \\
\texttt{view[2]=SwingGui} \\

\subsection{Flashlists}
A list of flashlists to use. \\
\texttt{flashlists=levelZeroFM\_subsys;EVM;frlcontrollerLink;frlcontrollerCard;levelZeroFM\_static;gt\_cell\_lumiseg;FMMInput;jobcontrol;EventProcessorStatus;StorageManagerPerformance;FMMStatus;hostInfo}

Blacklisting specified fields per flashlist.\\
\texttt{blacklist\_jobcontrol=jobTable}
blacklist\_frlcontrollerCard=myrinetProcFile,myrinetBadEventNumber
blacklist\_levelZeroFM\_subsys=FEDS


\subsubsection{Others}
Defines a period to play the data back for. \\
\texttt{timerStart=1383763860000} \\
\texttt{timerEnd=1383763860800} \\

Data format is used when converting timestamp strings into numeric values. \\
\texttt{dateFormat=yyyy-MM-dd'T'HH:mm:ss.SSS} \\

Output directory is the location that \texttt{FileSink} writes into. \\
\texttt{outputDir=/home/bawey/load/} \\

Classes to be registered as log sinks
\texttt{logSinks="ch.cern.cms.load.sinks.SwingGui";}

